\documentclass[12pt]{pom_thesis}

\author{Firstname Lastname}
\advisor{Firstname Lastname}
\title{My Bibliography, Presented in an Excessively Formal Way}

\begin{document}

\maketitle

\begin{abstract}In this paper we don't really do much.  However, there are a lot of {\it real} theorems that still need to be proved. That is what you will probably do in your thesis. For now we have the bibliography.
\end{abstract}

\pagenumbering{roman}
\tableofcontents

\newpage
\pagenumbering{arabic}
% this is how you begin a chapter:
% the label is so that you can refer to it later
\begin{chapter}{Or, I was too lazy to delete the entire template}
\label{Intro}
\section{Annotated Bibliography}



One of my main sources will be a textbook on the subject of Community-Based Operations Research (CBOR). Most of the book consists of specific case studies in the field of operations research, including certain papers that are basically reproduced in their entirety in the textbook. The textbook itself is split into four sections: ``Models and Analytic Methods," ``Facility Location and Spatial Analysis," ``Minorities and Disadvantaged Groups," and ``Service Delivery." I will initially focus on one specific case study presented in this textbook to give me a better understanding of what CBOR looks like in practice. See \cite{MJ12} \newline \newline 


For the next textbook I have a classic Operations Research book. This takes a more traditional approach to the more traditional part of the discipline. This book will be mainly used to look at fundamental ideas (linear programs, simplex method, etc). See \cite{FHGL} \newline \newline 

This paper describes a course taught at the College of Business and Administration at Drexel University in which students undertook real-world projects in inner-city neighborhoods. They addressed public sector issues such as people moving, traffic flow, trash removal, market promotion, and surveys. These problems are complex and have many stakeholders with competing interests, so they don't fit into the traditional course work provided in the field. Naturally, this paper is of interest to me because this is what I'm trying to research. See \cite{SBHM}

Bada Bing Bada boom

% you should close a chapter before beginning a new one!
\end{chapter}


\bibliographystyle{apalike}
\bibliography{thesis_test_bib}


\end{document}

