\documentclass[12pt]{pom_thesis}

\author{Firstname Lastname}
\advisor{Firstname Lastname}
\title{Thesis Outline}

\begin{document}

\maketitle

\begin{abstract}In this paper we don't really do much.  However, there are a lot of {\it real} theorems that still need to be proved. That is what you will probably do in your thesis. For now we have the thesis outline.
\end{abstract}

\pagenumbering{roman}
\tableofcontents

\newpage
\pagenumbering{arabic}
% this is how you begin a chapter:
% the label is so that you can refer to it later
\begin{chapter}{Introduction}
\label{Intro}
\section{What will go here?}

In the introduction I will explain the history of operations research and how it tends to be most utilized in the private sector. I will detail the development of (and necessity for) community-based operations research, and then explain that I will be examining a particular case study: the problem of developing new public parks in Bogot\'a, Colombia. I will perhaps provide a literature review here, a roadmap of what I will cover in the rest of the thesis, and anything else that may fit and come to mind later.

% you should close a chapter before beginning a new one!
\end{chapter}

\begin{chapter}{Toy Example}
\section{What is a toy example?}

In this chapter I will present a simplified version of the model I will be observing. We will take the problem of park allocation and make it significantly easier to understand. We will have less variables, which I will present and explain, as well as less objective functions (since the actual model has six objective functions), and possibly even less constraints. I will walk through the problem explanation, present any relevant information, formulate the model, and solve it. We move on to the real model.
\end{chapter}

\begin{chapter}{The Model}
\section{What model?}
In here I will actually look at the model, taken straight from the paper I am reading. I will expand upon the toy example, explain the actual situation in more detail, and make note of the extra constraints and objective functions that we will take into account. I will present the mathematical formulation of the model, and examine the solution. Perhaps I will make commentary on particular decisions and assumptions the modelers made when constructing their model.
\end{chapter}

\begin{chapter}{Multiobjective Facility Location Problems}
\section{What?}
Here we will look at the general class of Multiobjective facility location problems, which is the class of problems that contains the main model/problem I will be looking at for my thesis. 
\end{chapter}

\begin{chapter}{Discrete Facility Location Problems}
\section{What? pt. II}
The problem I will be examining also falls under this category. I am not sure how much this would vary from the previous chapter. But if it turns out there is a significant difference between both types of problems, it might be helpful to provide a dedicated chapter for both. Maybe the only difference is that the other class of problems has many objective functions.
\end{chapter}

\begin{chapter}{Applications}
If I have time to apply what I have learned to another problem, maybe this will go here. But this may be a bit ambitious. Stay tuned.
\end{chapter}

\end{document}

 